The Migration of the Field Code

### 2016-02-19 index.Rmd
Update project hub

---
title: "Analysis of Text Reuse in the Field Code"
author: "Lincoln Mullen and Kellen Funk"
---

This is an analysis notebook for detecting text reuse in codes of civil procedure---the "Field codes"---in the nineteenth-century United States. It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com).

>>>>

---
title: "The Migration of the Field Code"
author: "Kellen Funk and Lincoln Mullen"
---

This is an analysis notebook for detecting text reuse in legal codes of civil procedure---the "Field codes"---in the nineteenth-century United States. It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com). This [working paper](talks/dh-working-group/dh-working-group.pdf) has the most up-to-date summary of what we are doing.
